Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Add a citation for HMM handwriting recognition

\section{Technology}
We have begun implementation of the Nell system.  In this section we
will describe the implementation of three of the most novel pieces
from the software engineering side.  These are not necessarily the
most novel-appearing from the user's perspective: for example, the
handwriting UI is still fairly unusual in consumer devices, but the
implementation of a separated-character handwriting recognition engine
using Hidden Markov Models is well-understood.
\textbf{SMOOTH THIS LANGUAGE}

>>>>

\section{Technology}
We have begun implementation of the Nell system.  In this section we
will describe the implementation of three of the most novel pieces
from the software engineering side.  These are not necessarily the
most novel-appearing from the user's perspective: for example, the
handwriting UI is still fairly unusual in consumer devices, but the
implementation of a separated-character handwriting recognition engine
using Hidden Markov Models is well-understood~\cite{hanshu:handwriting}.
\textbf{SMOOTH THIS LANGUAGE}
